Taxonomic bias can create spurious results in microbiome differential-abundance analyses unless it is properly accounted for

### 2021-05-11 index.Rmd
Edit frontmatter
Update authors, title, and preface to account for the article

---
title: "Characterizing and mitigating the effects of experimental bias on differential (absolute) abundance analysis in microbiome studies"
author: "Michael R. McLaren"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [main.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: mikemc/bda-theory
description: "Mathematical theory of the effects of experimental bias on differential (relative and absolute) abundance analysis in microbiome studies."
---

# Abstract

This monograph develops a mathematical theory of the effects of protocol- and taxon-specific experimental bias on various types of differential (relative and absolute) abundance analyses in microbiome studies and uses it to formulate several mitigation strategies.

>>>>

---
title: "Taxonomic bias can create spurious results in microbiome differential-abundance analyses unless it is properly accounted for"
author:
  - Michael R. McLaren^[North Carolina State University; send correspondence to m.mclaren42@gmail.com]
  - Karen G. Lloyd^[University of Tennessee]
  - Benjamin J. Callahan^[North Carolina State University]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [main.bib, packages.bib]
biblio-style: apalike
link-citations: yes
# description:
github-repo: mikemc/bda-theory
---

# Preface {-}

This manuscript addresses the effect that the taxonomic bias inherent in microbiome measurement has on microbial differential-abundance analysis.
We describe the basic problem posed by taxonomic bias for measuring changes in the abundance of particular taxa across conditions and describe new strategies for mitigating the errors it induces.
Analyses of both relative and absolute abundances are considered.
In its current form, the manuscript sits somewhere between a standard scientific article and a monograph; 
it consists of an article followed by a series of appendices which together give a comprehensive treatment of the implications of the @mclaren2019cons model of taxonomic bias for differential-abundance analysis and experimental design.
It is licensed under a [CC BY 4.0 License](https://creativecommons.org/licenses/by/4.0/).
See [the Zenodo record](https://doi.org/10.5281/zenodo.4552717) for how to cite the latest version.
